---
title       : Stock Analysis
subtitle    : Stock Analysis with Quantmod
author      : Tam Nguyen Chinh Ho
job         : Project Manager
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Stock Analysis Introduction
- The application to utilize library quantmod in order to:
  > - Stock Analysis and Prediction : SAP
  > - Polling stock data from some providers
  > - Analyze data and output with trend charts from varies of durations: all, 1 month, 3 months, 6 months, 1 year
  > - Add finance indicators in order to have the better information to decide and predict more precisely for the stock quote next prices

- The target of this application is to predict the stock value --> we can extend by adding machine learning for this purpose. With this application, user can:
  > - Select a stock symbol
  > - Select an interested analysis duration
  > - Select technical indicators

--- .class #Stock Analysis Introduction

## Stock Analysis Introduction - Cont 1
- User can select the interest duration via slider bar
- User can view the downloaded data from server and download to local PC
- The application is in opened status, which is still needed to receive ideas, comments, feedbacks and even community contributions
- Application is simple and in draft version, enough for demonstration the idea only

--- .class #Stock Analysis Introduction - Cont 1


## Quantmod library overview

- Quantitative Financial Modelling & Trading Framework
- Designed to assist the quantitative trader in the development, testing, and deployment of statistically based trading models
- Provide a series of technical indicator which helps investors to get more information for their decisions

--- .class #Quantmod library overview

## How SAP work - Getting and Filtering data

```{r, echo=FALSE}
library(quantmod)

downloadSymbol <- function(environment, symbol) {
  if (is.null(environment[[symbol]])) {
    environment[[symbol]] <- getSymbols(symbol, auto.assign = FALSE)
  }
  
  environment[[symbol]]
}

```

- Download the stock data

```{r, echo=TRUE, message=FALSE}
# To initialize and new environment for caching purpose
system_environment <- new.env()
symbol_data <- downloadSymbol(system_environment, "AAPL")
```

- Filter data via a specific duration
```{r, echo=TRUE}
in_duration_data <- last(symbol_data, "3 months")
```

--- .class #How SAP work - Getting and Filtering data


## How SAP work - Plotting result

- Render candle chart and Add technical indicators

```{r, echo=FALSE, message=FALSE}
library(quantmod)

plot <- candleChart(in_duration_data, name = "AAPL", multi.col=TRUE, theme = "white")
addBBands(plot)
addEVWMA(plot)
print(plot)
```

--- .class #How SAP work - Plotting result
